### 2021-02-11 abstract.tex
Migrate from Overleaf version 3920
Update to the current head in Overleaf.

Overleaf label: "Migrate to Git"

https://www.overleaf.com/project/5f75a50ba1a0930001ce1162

This paper describes and evaluates a symbol precedence heuristic based on a \acrlong{gcn}.
When trained on proof attempts with random symbol precedences,
the heuristic outperforms the state of the art by more than 20~\%.
For the purpose of the evaluation, the symbol precedences predicted by the heuristic
are used to instantiate Knuth-Bendix term simplification orderings.
These orderings in turn guide the proof search in the state-of-the-art \acrlong{atp} \vampire{}
by constraining the superposition calculus inferences.
The evaluation is performed on \acrlong{fol} problems from the TPTP problem library.

>>>>

This paper describes and evaluates a symbol precedence heuristic based on a \acrlong{gcn}.
When trained on proof attempts with random symbol precedences,
the heuristic outperforms the state of the art by more than \SI{2}{\percent}.
For the purpose of the evaluation, the symbol precedences predicted by the heuristic
are used to instantiate Knuth-Bendix term simplification orderings.
These orderings in turn guide the proof search in the state-of-the-art \acrlong{atp} \vampire{}
by constraining the superposition calculus inferences.
The evaluation is performed on \acrlong{fol} problems from the \acrshort{tptp} problem library.

\keywords{saturation-based theorem proving \and
term simplification ordering \and
symbol precedence \and
\acrlong{ml} \and
\acrlong{gcn}}

### 2021-02-11 introduction.tex
Migrate from Overleaf version 3920
Update to the current head in Overleaf.

Overleaf label: "Migrate to Git"

https://www.overleaf.com/project/5f75a50ba1a0930001ce1162

The state-of-the-art \gls{fol} \glspl{atp},
such as \vampire{} \cite{10.1007/978-3-642-39799-8_1} and E \cite{10.1007/978-3-030-29436-6_29},
are saturation-based and
infer new provable clauses by applying the rules of \definiendum{superposition calculus}.
\todo[author=Filip]{Cite some source that explains superposition calculus.}
The inferences under superposition calculus are constrained by a \definiendum{simplification ordering on the terms}.
\todo[author=Filip]{Do we mean terms in sensu stricto (applications of functions), or generalized terms (applications of functions and predicates)?}
The two classes of simplification orderings commonly used in practice are
\gls{lpo} \cite{Kamin1980} and \gls{kbo} \cite{Knuth1983}.
In both classes the ordering is specified by a \definiendum{symbol precedence},
\todo[author=Filip]{This may be an oversimplification: KBO is further parameterized by symbol weights.}
which is a permutation of predicate and function symbols of the input problem.

>>>>

The state-of-the-art \gls{fol} \glspl{atp},
such as \vampire{} \cite{10.1007/978-3-642-39799-8_1} and E \cite{10.1007/978-3-030-29436-6_29},
are saturation-based and
infer new provable clauses by applying the rules of the \definiendum{superposition calculus}.
\todo[author=Filip]{Cite some source that explains superposition calculus.}
The inferences under superposition calculus are constrained by a \definiendum{simplification ordering on the terms}.
\todo[author=Filip]{Do we mean terms in sensu stricto (applications of functions), or generalized terms (applications of functions and predicates)?}
The two classes of simplification orderings commonly used in practice are
\gls{lpo} \cite{Kamin1980} and \gls{kbo} \cite{Knuth1983}.
In both classes the ordering is specified by a \definiendum{symbol precedence},
\todo[author=Filip]{This may be an oversimplification: KBO is further parameterized by symbol weights.}
which is a permutation of predicate and function symbols of the input problem.
